---
title: "Recruitment Bias Adjustment in Ricker Model"
#output: html_document
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Ricker model in BAM, SS, and AMAK and the conversion function
### 1.1 BAM method  

E1: $R_{y+1}=\frac{S_y}{\phi_0}exp(h(1-\frac{S_y}{R_0\phi_0}))$

E2: $R_{eq}=\frac{R_0}{\phi_F/\phi_0}(1+\frac{log(BC_{BAM}\times \phi_F/\phi_0)}{h})$

Here, virgin recruitment $R_{0}$ and steepness $h$ are median values, and $BC_{BAM}=exp(\sigma_R^2/2)$

### 1.2 SS method

E3: $R_{y+1}=\frac{S_y}{\phi_0}exp(h(1-\frac{S_y}{R_0\phi_0}))\times BC_{SS}$

E4: $R_{eq}=\frac{R_0}{\phi_F/\phi_0}(1+\frac{log(\phi_F/\phi_0)}{h})$

Here, virgin recruitment $R_{0}$ and steepness $h$ are mean values, and $BC_{SS}=exp(-\sigma_R^2/2)$

### 1.3 AMAK method (To be compared...)

E5: $R_{y+1}=\frac{S_{y}}{\phi_{0}}exp(\alpha(1-\frac{S_{y}}{R_{0}\phi_{0}}))$

E6: $\alpha=log(\frac{-4h}{h-1})$

### 1.4 Compare BAM and SS estimates following Erik's method
```{r, echo=FALSE}
R0_med_true=1000000     # true median R0 value
h_med_true=0.75   # vector of median steepness (h) values
phi0=0.01025625

sd.val=0.6
BC=(sd.val^2)/2

n=100000 # use a fairly large number because fits need be very tight

S0_med_true=R0_med_true*phi0

#S.vec=runif(n,min=0,max=S0)
S.vec=seq(0.001,S0_med_true, length=n)

R.vec.true=S.vec/phi0*exp(h_med_true*(1-S.vec/(R0_med_true*phi0)))
lnormdev.vec=rlnorm(n,0,sd.val)
R.vec.obs=R.vec.true*lnormdev.vec

# median S-R fit (produces median R0 and h, used in BAM)
SR.fit.med=function(par){
  R0.par=par[1]
  h.par=par[2]
  R.vec.pred=S.vec/phi0*exp(h.par*(1-S.vec/(R0.par*phi0)))
  resid=(log(R.vec.obs)-log(R.vec.pred))^2 # median likelihood
  resid.out=sum(resid)
  resid.out}

# SS S-R fit (produces mean R0 and h, used in SS)
SR.fit.SS=function(par){
  R0.par=par[1]
  h.par=par[2]
  R.vec.pred=S.vec/phi0*exp(h.par*(1-S.vec/(R0.par*phi0)))*exp(-BC)
  resid=(log(R.vec.obs)-log(R.vec.pred))^2 # median likelihood
  resid.out=sum(resid)
  resid.out}

#optimization for SR parameters using mean and median fit criteria
fit.med=optim(c(R0_med_true,h_med_true),SR.fit.med,lower=c(0,0.2),method="L-BFGS-B",upper=c(3*R0_med_true,1.0))
fit.SS=optim(c(R0_med_true,h_med_true),SR.fit.SS,lower=c(0,0.2),method="L-BFGS-B",upper=c(3*R0_med_true,1.0))

R0.BAM=fit.med$par[1]
h.BAM=fit.med$par[2]

R0.SS=fit.SS$par[1]
h.SS=fit.SS$par[2]
S0.SS=R0.SS*phi0

phiF=seq(from=1.5,to=8,by=0.1)

# SS method
Seq.SS=S0.SS*(1.+(log(R0.SS/S0.SS)+log(phiF))/h.SS);
Req.SS=R0.SS*Seq.SS/S0.SS * exp(h.SS*(1.-Seq.SS/S0.SS));
# BAM method
#Req.BAM=R0.BAM*(exp(BC)*4*h.BAM*phiF-(1-h.BAM)*phi0)/((5*h.BAM-1)*phiF)
Req.BAM=R0.BAM/(phiF/phi0)*(1+log(exp(BC)*phiF/phi0)/h.BAM)
Seq.BAM=Req.BAM*phiF

cat(paste("True_Median_R0=", R0_med_true, sep=""),
    paste("True_Median_h=", h_med_true, sep=""),
    paste("BAM_Median_R0=", R0.BAM, sep=""), 
    paste("BAM_Median_h=", h.BAM, sep=""), 
    paste("SS_Mean_R0=", R0.SS, sep=""),
    paste("SS_Mean_h=", h.SS, sep=""),
    sep="\n")

plot(phiF, Req.BAM, col="red", pch=1, type="o", lty=1, xlab="phiF", ylab="Req")
lines(phiF, Req.SS, col="deepskyblue3", pch=3, type="o", lty=2)
legend("topright",
       legend=c("BAM_Req", "SS_Req"), 
       col=c("red", "deepskyblue3"), 
       lty=c(1, 2),
       pch=c(1, 3),
       bty="n")
```

Figure 1. Equilibrium R over phiF from BAM (red solid line) and SS (blue dash line). **It demonstrates that with correct conversion from median to mean values, BAM and SS should produce almost identical estimates.**  

### 1.5 Conversion function
#### 1.5.1 The conversion function following Chris's method
```{r, echo=TRUE}
convertSRparms <- function(R0, h, phi, sigmaR, mean2med){
  BC <- ifelse(mean2med == TRUE, exp(-0.5 * sigmaR^2), exp(0.5 * sigmaR^2))
  S0BC <- R0 * phi * (1 + log(BC) / h)
  R0BC <- S0BC / phi
  Rnew <- BC * 0.2 *S0BC / phi * exp(h * (1 - 0.2 * S0BC/ (R0 * phi)))
  hBC <- Rnew /R0BC
  return(list(S0BC = S0BC, R0BC = R0BC, hBC = hBC))
}
```

#### 1.5.2 Inputs (Median R0, median h, phi, sigmaR, mean2med) and outputs (Mean R0BC and mean hBC)
```{r, echo=FALSE}
R0 <- R0_med_true
h <- h_med_true
phi <- phi0
sigmaR <- sd.val
mean2med <- FALSE
p <- convertSRparms(R0, h, phi, sigmaR, mean2med)
```

```{r, echo=FALSE}
cat(paste("R0=", R0, sep=""), 
    paste("h=", h, sep=""), 
    paste("phi=", phi, sep=""),
    paste("sigmaR=", sigmaR, sep=""),
    paste("mean2med=", mean2med, sep=""),
    paste("R0BC=", p$R0BC, sep=""),
    paste("hBC=", p$hBC, sep=""),
    sep="\n")
```

**The converted mean steepness (hBC) is different compared to the SS_Mean_h from section 1.4.**

#### 1.5.3 Validation check
```{r, echo=TRUE}
BC <- ifelse(mean2med == TRUE, exp(-0.5 * sigmaR^2), exp(0.5 * sigmaR^2))
S.vec <- seq(0, R0 * phi, length.out = 1000)
R.vec <- S.vec / phi * exp(h * (1 - S.vec/ (R0 * phi)))
R.vecBC <- R.vec * BC
R.calc <- S.vec / phi * exp(p$hBC * (1 - S.vec / (p$R0BC * phi)))
diff <- R.calc - R.vecBC
range(diff)
plot(S.vec, R.vecBC, col="red", xlab="SSB", ylab="R", type="l", lty=1)
lines(S.vec, R.calc, col="deepskyblue3", lty=2)
legend("topleft", 
       legend=c("BAM_R", "SS_R"), 
       col=c("red", "deepskyblue3"), 
       lty=c(1,2),
       bty="n")
```

Figure 2. Mean recruitment over SSB from BAM (red solid line) and SS (blue dash line). **The estimates from BAM and SS are not identical like the results from section 1.4. The conversion of steepness needs to be checked, so I read Dorn 2002 paper to seek a solution.**

## 2. Ricker model from Dorn 2002 and the conversion function
### 2.1 Curvature parameters $\alpha$ and steepness $h$ from Dorn 2002

The Ricker curve with paramters median virgin recruitment $R_{0}$ and curvature parameter $\alpha$ is

E7: $R_{y+1}=\frac{S_{y}}{\phi_{0}}exp(\alpha(1-\frac{S_{y}}{R_{0}\phi_{0}}))$

The steepness $h$ from Dorn 2002 is

E8: $h=\frac{\frac{0.2S_{y}}{\phi_{0}}exp(\alpha(1-\frac{0.2S_{y}}{R_{0}\phi_{0}}))}{\frac{S_{y}}{\phi_{0}}exp(\alpha(1-\frac{S_{y}}{R_{0}\phi_{0}}))}$

E9: $h=0.2exp(\alpha(1-\frac{0.2S_{y}}{R_{0}\phi_{0}})-\alpha(1-\frac{S_{y}}{R_{0}\phi_{0}}))$

E10: $h=0.2exp(\frac{0.8S_{0}\alpha}{R_{0}\phi_{0}})=0.2exp(0.8\alpha)$

The curvature parameter $\alpha$ from Dorn 2002 is

E11: $\alpha=\frac{log(5h)}{0.8}=1.25log(5h)$

The equations were derived following [Mangel et al. 2009](https://www.researchgate.net/publication/267878032_Estimating_stock-recruitment_steepness_from_life_history_information_A_case_study_of_north_Pacific_bluefin_tuna_Thunnus_orientalis) and [Sampson 2008](http://oregonstate.edu/instruct/fw431/sampson/LectureNotes/15-Recruitment3.pdf).

The $\alpha$ from Dorn 2002 is equivalent to the steepness $h$ in BAM and SS (E1-E4).

```{r, echo=FALSE}
alpha=seq(0.2, 1, by=0.01)
h=0.2*exp(alpha*0.8)
par(mfrow=c(1,2))
plot(alpha, h, xlab="alpha", ylab="h", pch=16, cex=0.5)
plot(alpha, alpha-h, xlab="alpha", ylab="alpha-h", pch=16, cex=0.5)
abline(h=0)
```

Figure 3. The difference between $\alpha$ and steepness $h$ in the Ricker model from Dorn 2002.

### 2.2 The final conversion function with consideration of conversion between $\alpha$ and true steepness $h$ in Dorn 2002: 

**hBC <- 1.25*log(5*Rnew /R0BC)**

```{r, echo=TRUE}
convertSRparms <- function(R0, h, phi, sigmaR, mean2med){
  BC <- ifelse(mean2med == TRUE, exp(-0.5 * sigmaR^2), exp(0.5 * sigmaR^2))
  S0BC <- R0 * phi * (1 + log(BC) / h)
  R0BC <- S0BC / phi
  Rnew <- BC * 0.2 *S0BC / phi * exp(h * (1 - 0.2 * S0BC/ (R0 * phi)))
  hBC <- 1.25*log(5*Rnew /R0BC)
  return(list(S0BC = S0BC, R0BC = R0BC, hBC = hBC))
}
```

### 2.3 Inputs (Median R0, median h, phi, sigmaR, mean2med) and outputs (Mean R0BC and mean hBC)
```{r, echo=FALSE}
R0 <- R0_med_true
h <- h_med_true
phi <- phi0
sigmaR <- sd.val
mean2med <- FALSE
p <- convertSRparms(R0, h, phi, sigmaR, mean2med)
```

```{r, echo=FALSE}
cat(paste("R0=", R0, sep=""), 
    paste("h=", h, sep=""), 
    paste("phi=", phi, sep=""),
    paste("sigmaR=", sigmaR, sep=""),
    paste("mean2med=", mean2med, sep=""),
    paste("R0BC=", p$R0BC, sep=""),
    paste("hBC=", p$hBC, sep=""),
    sep="\n")
```

**The converted mean steepness (hBC) is the same compared to the SS_Mean_h from section 1.4.**

### 2.4 Validation check
```{r, echo=TRUE}
BC <- ifelse(mean2med == TRUE, exp(-0.5 * sigmaR^2), exp(0.5 * sigmaR^2))
S.vec <- seq(0, R0 * phi, length.out = 1000)
R.vec <- S.vec / phi * exp(h * (1 - S.vec/ (R0 * phi)))
R.vecBC <- R.vec * BC
R.calc <- S.vec / phi * exp(p$hBC * (1 - S.vec / (p$R0BC * phi)))
diff <- R.calc - R.vecBC
range(diff)
plot(S.vec, R.vecBC, col="red", xlab="SSB", ylab="R", type="l", lty=1)
lines(S.vec, R.calc, col="deepskyblue3", lty=2)
legend("topleft", 
       legend=c("BAM_R", "SS_R"), 
       col=c("red", "deepskyblue3"), 
       lty=c(1,2),
       bty="n")
```

Figure 4. Mean recruitment over SSB from BAM (red solid line) and SS (blue dash line). **The estimates from BAM and SS are identical, like the results from section 1.4. The final conversion function is correct.**

### 2.5. Median and mean virgin recruitment and steepness over a range of steepness and sigmaR
```{r, echo=FALSE}
R0=1000000
phi=0.01025625
sigmaR=seq(0.01, 2, by=0.01)
h=seq(0.21, 1, by=0.01)

R0diff <- hdiff <- matrix(NA, nrow=length(sigmaR), ncol=length(h))

for(i in 1:length(sigmaR)){
  for(j in 1:length(h)){
    R0diff[i,j] <- (convertSRparms(R0=R0, h=h[j], phi=phi, sigmaR=sigmaR[i], mean2med=FALSE)$R0BC-R0)/R0*100
    hdiff[i,j] <- (convertSRparms(R0=R0, h=h[j], phi=phi, sigmaR=sigmaR[i], mean2med=FALSE)$hBC-h[j])
  }
}

filled.contour(sigmaR, h, R0diff,
               color = terrain.colors,
               xlab="SigmaR", ylab="Median h",
               plot.axes = {
                 axis(1); axis(2);
                 contour(sigmaR, h, R0diff,
                         col = "black",
                         add = TRUE,
                         levels = c(10, 50, 100, 300, 500, 800),
                         method="edge")
                 },
               key.title = {
                 par(cex.main=0.8);
                 title(main="Relative Diff\nin R0 (%)")
                 })
legend("topleft", "A)", bty="n", box.col = "")

filled.contour(sigmaR, h, hdiff,
               color = terrain.colors,
               xlab="SigmaR", ylab="Median h",
               plot.axes = {
                 axis(1); axis(2);
                 contour(sigmaR, h, hdiff,
                         col = "black",
                         add = TRUE,
                         levels = c(0.1, 0.4, 0.8, 1.2, 1.6),
                         method="edge")
                 },
               key.title = {
                 par(cex.main=0.8);
                 title(main="Diff in h")
               })
legend("topleft", "B)", bty="n", box.col = "")

```

Figure 5. A) Relative difference in virgin recruitment (%; $\frac{(meanR_0 - medianR_0)}{medianR_0}×100$) over possible combination of median steepness and standard deviation of recruitment using the stock-recruitment parameters conversion function. B) Difference in steepness ($mean_h - median_h$) over possible combination of median steepness and standard deviation of recruitment using the stock-recruitment parameters conversion function.