---
title: "Mean- VS. Median-unbiased stock-recruit parameters in Operating model"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### **R Markdown File Link:**

https://github.com/Bai-Li-NOAA/Age_Structured_Stock_Assessment_Model_Comparison/blob/full-features/ASSAMC/docs/MedianMeanSRparamsOM.Rmd 

## 1. Operating Model with median- or mean-unbiased stock-recruit parameters
### 1.1 Mean-unbiased stock-recruit parameters

* Beverton-Holt Model

E1: $R_{y+1}=\frac{0.8R_0hS_y}{0.2R_0\phi_0(1-h)+S_y(h-0.2)}\times BC_{mean}$

E2: $R_{eq}=\frac{R_0(4h\phi_F-(1-h)\phi_0)}{(5h-1)\phi_F})$

Here, virgin recruitment $R_{0}$ and steepness $h$ are mean values, and $BC_{mean}=exp(-\sigma_R^2/2)$

* Ricker model

E3: $R_{y+1}=\frac{S_y}{\phi_0}exp(h(1-\frac{S_y}{R_0\phi_0}))\times BC_{mean}$

E4: $R_{eq}=\frac{R_0}{\phi_F/\phi_0}(1+\frac{log(\phi_F/\phi_0)}{h})$

Here, virgin recruitment $R_{0}$ and steepness $h$ are mean values, and $BC_{mean}=exp(-\sigma_R^2/2)$

### 1.2 Median-unbiased stock-recruit parameters

* Beverton-Holt Model

E5: $R_{y+1}=\frac{0.8R_0hS_y}{0.2R_0\phi_0(1-h)+S_y(h-0.2)}$

E6: $R_{eq}=\frac{R_0(BC_{median}4h\phi_F-(1-h)\phi_0)}{(5h-1)\phi_F})$

Here, virgin recruitment $R_{0}$ and steepness $h$ are mean values, and $BC_{median}=exp(\sigma_R^2/2)$

* Ricker model

E7: $R_{y+1}=\frac{S_y}{\phi_0}exp(h(1-\frac{S_y}{R_0\phi_0}))$

E8: $R_{eq}=\frac{R_0}{\phi_F/\phi_0}(1+\frac{log(BC_{median}\times \phi_F/\phi_0)}{h})$

Here, virgin recruitment $R_{0}$ and steepness $h$ are median values, and $BC_{median}=exp(\sigma_R^2/2)$

## 2. Simulated population with Beverton-Holt model 

```{r, echo=FALSE, message=FALSE}
# install.packages("remotes")
# install.packages("devtools")
# remotes::install_github(repo="Bai-Li-NOAA/Age_Structured_Stock_Assessment_Model_Comparison", ref="full-features", force = TRUE)
# library(ASSAMC)
setwd("C:/Users/bai.li/Documents/Github/Age_Structured_Stock_Assessment_Model_Comparison/ASSAMC/")
devtools::load_all()
## Setup working directory
maindir <- "C:/Users/bai.li/Desktop/bias_adjustment"

om_sim_num <- 100 # total number of iterations per case
keep_sim_num <- 100 # number of kept iterations per case
figure_number <- 10 # number of individual iteration to plot

seed_num <- 9924

#### Life-history parameters ####
year <- 1:100
ages <- 1:12   #Age structure of the popn

initial_equilibrium_F <- TRUE
median_R0 <- NULL #Average annual unfished recruitment (scales the popn)
median_h <- NULL #Steepness of the Beverton-Holt spawner-recruit relationship.
mean_R0 <- 1000000
mean_h <- 0.21
SRmodel <- 1 # 1=Beverton-Holt; 2=Ricker
M <- 0.6       #Age-invariant natural mortality

Linf <- 800	  #Asymptotic average length
K <- 0.18     	#Growth coefficient
a0 <- -1.36    #Theoretical age at size 0
a.lw <- 0.000000025  #Length-weight coefficient
b.lw <- 3.0     	    #Length-weight exponent
A50.mat <- 2.25      #Age at 50% maturity
slope.mat <- 3       #Slope of maturity ogive
pattern.mat <- 1     #Simple logistic maturity
female.proportion <- 0.5   #Sex ratio

#### Fleet settings ####
fleet_num <- 1

#CV of landings for OM
cv.L <- list()
cv.L$fleet1 <- 0.005

#Input CV of landings for EMs
input.cv.L <- list()
input.cv.L$fleet1 <- 0.01

#Annual sample size (nfish) of age comp samples
n.L <- list()
n.L$fleet1 <- 200

#Define fleet selectivity
sel_fleet <- list()

sel_fleet$fleet1$pattern <- 1
sel_fleet$fleet1$A50.sel1 <- 2
sel_fleet$fleet1$slope.sel1 <- 1

#### Survey settings ####
survey_num <- 1

#CV of surveys for OM
cv.survey <- list()
cv.survey$survey1 <- 0.1

#Input CV of surveys for EMs
input.cv.survey <- list()
input.cv.survey$survey1 <- 0.2

#Annual sample size (nfish) of age comp samples
n.survey <- list()
n.survey$survey1 <- 200

#Define survey selectivity
sel_survey <- list()

sel_survey$survey1$pattern <- 1
sel_survey$survey1$A50.sel1 <- 1.5
sel_survey$survey1$slope.sel1 <- 2

#### Other settings ####
logf_sd <- 0.2
f_dev_change <- FALSE
f_pattern <- 1
start_val <- 0
middle_val <- NULL
end_val <- 0
f_val <- NULL
start_year <- 1
middle_year <- NULL

logR_sd <- 0.2
r_dev_change <- TRUE

om_bias_cor <- TRUE
bias_cor_method <- "mean_unbiased" #Options: "none", "median_unbiased", and "mean_unbiased"
em_bias_cor <- FALSE

mean_base_case <- save_initial_input(base_case=TRUE, case_name = "C0")

h_vec <- c(0.21, 0.4, 0.6, 0.8, 1)
logR_sd_vec <- seq(from=0.2, to=2, by=0.2)
```

* Forward projection without fishing mortality
* Simulation number = `r om_sim_num`
* Simulation model year = `r max(year)`
* Steepness $h$ tested: `r h_vec`
* Standard deviation of log recruitment $\sigma_R$: `r logR_sd_vec`
* M = `r M`

### 2.1 OM_Mean with mean-unbiased stock-recruit parameters

```{r, echo=FALSE}
meanh_vec <- h_vec
logR_sd_vec <- logR_sd_vec
forloop_id <- expand.grid(meanh_vec = meanh_vec, logR_sd_vec = logR_sd_vec)

depletion_list <- list()

for(i in 1:nrow(forloop_id)){
  updated_input <- save_initial_input(base_case=FALSE,
                                      input_list=mean_base_case,
                                      case_name="mean_case",
                                      mean_R0=1000000,
                                      mean_h=forloop_id$meanh_vec[i],
                                      logR_sd=forloop_id$logR_sd_vec[i],
                                      om_bias_cor=TRUE,
                                      bias_cor_method="mean_unbiased")
  run_om(input_list=updated_input , show_iter_num=F)
  depletion <- matrix(NA, nrow=updated_input$om_sim_num, ncol=length(updated_input$year))
  for(j in 1:updated_input$om_sim_num){
    load(file.path(updated_input$maindir, updated_input$case_name, paste("output/OM/OM", j, ".RData", sep="")))
    depletion[j,] <- om_output$SSB/(om_input$mean_R0*om_input$Phi.0)
  }
  depletion_list[[i]] <- depletion
}

save(depletion_list, file=file.path(maindir, "mean_depletion_list.RData"))
```

* Known mean $R_0$ and $h$ -> OM_Mean -> $SSB$/$S0_{mean}$
* Mean steepness $h$ tested: `r meanh_vec`
* Standard deviation of log recruitment $\sigma_R$: `r logR_sd_vec`

```{r, echo=FALSE}
load(file.path(maindir, "mean_depletion_list.RData"))
par(mfrow=c(3, 2), mar=c(4,4,1,1))
color <- rainbow(length(logR_sd_vec))
for(i in 1:length(meanh_vec)){
  plot(apply(depletion_list[[which(forloop_id$meanh_vec==meanh_vec[i])[1]]], 2, mean), ylim=c(0,2), xlab="Year", ylab="Mean SSB/SSB0", type="l", col=color[1])
  for(j in 1:length(logR_sd_vec)){
    lines(apply(depletion_list[[which(forloop_id$meanh_vec==meanh_vec[i])[j]]], 2, mean), col=color[j])
  }
  abline(h=1, col="gray", lty=2)
  legend("topleft", paste("Mean h =", meanh_vec[i]), bty="n")
}
plot.new()
legend("top", 
         legend=logR_sd_vec,
         col=color,
         lty=rep(1, length(logR_sd_vec)),
         bty="n", 
         cex=0.8,
         ncol=3,
         title="SigmaR")
```

Figure 1. Temporal trend of mean (SSB/SSB_0) over `r om_sim_num` iteration runs under various combinations of steepness h and standard deviation of log recruitment sigmaR. 

### 2.2 OM_Median with median-unbiased stock-recruit parameters

```{r, echo=FALSE}
medianh_vec <- h_vec
logR_sd_vec <- logR_sd_vec
forloop_id <- expand.grid(medianh_vec = medianh_vec, logR_sd_vec = logR_sd_vec)

depletion_list <- list()

for(i in 1:nrow(forloop_id)){
  updated_input <- save_initial_input(base_case=FALSE,
                                      input_list=mean_base_case,
                                      case_name="median_case",
                                      median_R0=1000000,
                                      median_h=forloop_id$medianh_vec[i],
                                      mean_R0=NULL,
                                      mean_h=NULL,
                                      logR_sd=forloop_id$logR_sd_vec[i],
                                      om_bias_cor=TRUE,
                                      bias_cor_method="median_unbiased")
  run_om(input_list=updated_input , show_iter_num=F)
  depletion <- matrix(NA, nrow=updated_input$om_sim_num, ncol=length(updated_input$year))
  for(j in 1:updated_input$om_sim_num){
    load(file.path(updated_input$maindir, updated_input$case_name, paste("output/OM/OM", j, ".RData", sep="")))
    depletion[j,] <- om_output$SSB/(om_input$mean_R0*om_input$Phi.0)
  }
  depletion_list[[i]] <- depletion
}

save(depletion_list, file=file.path(maindir, "median_depletion_list.RData"))
```

* Known median $R_0$ and $h$ -> OM_Median -> $SSB$/$S0_{mean}$
* Median steepness $h$ tested: `r medianh_vec`
* Standard deviation of log recruitment $\sigma_R$: `r logR_sd_vec`

```{r, echo=FALSE}
load(file.path(maindir, "median_depletion_list.RData"))
par(mfrow=c(3, 2), mar=c(4,4,1,1))
color <- rainbow(length(logR_sd_vec))
for(i in 1:length(medianh_vec)){
  plot(apply(depletion_list[[which(forloop_id$medianh_vec==medianh_vec[i])[1]]], 2, mean), ylim=c(0,2), xlab="Year", ylab="Mean SSB/SSB0", type="l", col=color[1])
  for(j in 1:length(logR_sd_vec)){
    lines(apply(depletion_list[[which(forloop_id$medianh_vec==medianh_vec[i])[j]]], 2, mean), col=color[j])
  }
  abline(h=1, col="gray", lty=2)
  legend("topleft", paste("Median h =", medianh_vec[i]), bty="n")
}
plot.new()
legend("top", 
         legend=logR_sd_vec,
         col=color,
         lty=rep(1, length(logR_sd_vec)),
         bty="n", 
         cex=0.8,
         ncol=3,
         title="SigmaR")
```

Figure 2. Temporal trend of mean (SSB/SSB_0) over `r om_sim_num` iteration runs under various combinations of steepness h and standard deviation of log recruitment sigmaR. 

### 2.3 OM_Median with converted median-unbiased stock-recruit parameters from means

* Known mean $R_0$ and $h$ -> Convert to median $R_0$ and $h$ -> OM_Median -> $SSB$/$S0_{mean}$

```{r, echo=FALSE}
meanh_vec <- h_vec
logR_sd_vec <- logR_sd_vec
forloop_id <- expand.grid(meanh_vec = meanh_vec, logR_sd_vec = logR_sd_vec)

depletion_list <- list()
medianh_vec <- c()
medianR0_vec <- c()

for(i in 1:nrow(forloop_id)){
  updated_input <- save_initial_input(base_case=FALSE,
                                      input_list=mean_base_case,
                                      case_name="mean_case",
                                      mean_R0=1000000,
                                      mean_h=forloop_id$meanh_vec[i],
                                      logR_sd=forloop_id$logR_sd_vec[i],
                                      om_bias_cor=TRUE,
                                      bias_cor_method="median_unbiased")
  run_om(input_list=updated_input , show_iter_num=F)
  depletion <- matrix(NA, nrow=updated_input$om_sim_num, ncol=length(updated_input$year))
  for(j in 1:updated_input$om_sim_num){
    load(file.path(updated_input$maindir, updated_input$case_name, paste("output/OM/OM", j, ".RData", sep="")))
    depletion[j,] <- om_output$SSB/(om_input$mean_R0*om_input$Phi.0)
  }
  medianh_vec[i] <- convertSRparms(R0=om_input$mean_R0, 
                              h=om_input$mean_h, 
                              phi=om_input$Phi.0, 
                              sigmaR=om_input$logR_sd, 
                              mean2med=TRUE, 
                              model=om_input$SRmodel)$hBC
  medianR0_vec[i] <- convertSRparms(R0=om_input$mean_R0, 
                              h=om_input$mean_h, 
                              phi=om_input$Phi.0, 
                              sigmaR=om_input$logR_sd, 
                              mean2med=TRUE, 
                              model=om_input$SRmodel)$R0BC
  depletion_list[[i]] <- depletion
}

forloop_id$meanR0_vec <- rep(om_input$mean_R0, nrow(forloop_id))
forloop_id$converted_medianR0 <- medianR0_vec
forloop_id$converted_medianh  <- medianh_vec
forloop_id

save(depletion_list, file=file.path(maindir, "meanmedian_depletion_list.RData"))
```

```{r, echo=FALSE}
load(file.path(maindir, "meanmedian_depletion_list.RData"))
par(mfrow=c(3, 2), mar=c(4,4,1,1))
color <- rainbow(length(logR_sd_vec))
for(i in 1:length(meanh_vec)){
  plot(apply(depletion_list[[which(forloop_id$meanh_vec==meanh_vec[i])[1]]], 2, mean), ylim=c(0,2), xlab="Year", ylab="Mean SSB/SSB0", type="l", col=color[1])
  for(j in 1:length(logR_sd_vec)){
    lines(apply(depletion_list[[which(forloop_id$meanh_vec==meanh_vec[i])[j]]], 2, mean), col=color[j])
  }
  abline(h=1, col="gray", lty=2)
  legend("topleft", paste("Mean h =", meanh_vec[i]), bty="n")
}
plot.new()
legend("top", 
         legend=logR_sd_vec,
         col=color,
         lty=rep(1, length(logR_sd_vec)),
         bty="n", 
         cex=0.8,
         ncol=3,
         title="SigmaR")
```

Figure 3. Temporal trend of mean (SSB/SSB_0) over `r om_sim_num` iteration runs under various combinations of steepness h and standard deviation of log recruitment sigmaR. 

### 2.4 OM_Mean with converted mean-unbiased stock-recruit parameters from medians

* Known median $R_0$ and $h$ -> Convert to mean $R_0$ and $h$ -> OM_Mean -> $SSB$/$S0_{mean}$

```{r, echo=FALSE}
medianh_vec <- h_vec
logR_sd_vec <- logR_sd_vec
forloop_id <- expand.grid(medianh_vec = medianh_vec, logR_sd_vec = logR_sd_vec)

depletion_list <- list()
meanh_vec <- c()
meanR0_vec <- c()

for(i in 1:nrow(forloop_id)){
  updated_input <- save_initial_input(base_case=FALSE,
                                      input_list=mean_base_case,
                                      case_name="median_case",
                                      median_R0=1000000,
                                      median_h=forloop_id$medianh_vec[i],
                                      mean_R0=NULL,
                                      mean_h=NULL,
                                      logR_sd=forloop_id$logR_sd_vec[i],
                                      om_bias_cor=TRUE,
                                      bias_cor_method="mean_unbiased")
  run_om(input_list=updated_input , show_iter_num=F)
  depletion <- matrix(NA, nrow=updated_input$om_sim_num, ncol=length(updated_input$year))
  for(j in 1:updated_input$om_sim_num){
    load(file.path(updated_input$maindir, updated_input$case_name, paste("output/OM/OM", j, ".RData", sep="")))
    depletion[j,] <- om_output$SSB/(om_input$mean_R0*om_input$Phi.0)
  }
  depletion_list[[i]] <- depletion
  meanh_vec[i] <- convertSRparms(R0=om_input$median_R0, 
                              h=om_input$median_h, 
                              phi=om_input$Phi.0, 
                              sigmaR=om_input$logR_sd, 
                              mean2med=FALSE, 
                              model=om_input$SRmodel)$hBC
  meanR0_vec[i] <- convertSRparms(R0=om_input$median_R0, 
                              h=om_input$median_h, 
                              phi=om_input$Phi.0, 
                              sigmaR=om_input$logR_sd, 
                              mean2med=FALSE, 
                              model=om_input$SRmodel)$R0BC
}

save(depletion_list, file=file.path(maindir, "medianmean_depletion_list.RData"))

forloop_id$medianR0_vec <- rep(om_input$median_R0, nrow(forloop_id))
forloop_id$converted_meanR0 <- meanR0_vec
forloop_id$converted_meanh  <- meanh_vec
forloop_id
```

```{r, echo=FALSE}
load(file.path(maindir, "medianmean_depletion_list.RData"))
par(mfrow=c(3, 2), mar=c(4,4,1,1))
color <- rainbow(length(logR_sd_vec))
for(i in 1:length(medianh_vec)){
  plot(apply(depletion_list[[which(forloop_id$medianh_vec==medianh_vec[i])[1]]], 2, mean), ylim=c(0,2), xlab="Year", ylab="Mean SSB/SSB0", type="l", col=color[1])
  for(j in 1:length(logR_sd_vec)){
    lines(apply(depletion_list[[which(forloop_id$medianh_vec==medianh_vec[i])[j]]], 2, mean), col=color[j])
  }
  abline(h=1, col="gray", lty=2)
  legend("topleft", paste("Median h =", medianh_vec[i]), bty="n")
}
plot.new()
legend("top", 
         legend=logR_sd_vec,
         col=color,
         lty=rep(1, length(logR_sd_vec)),
         bty="n", 
         cex=0.8,
         ncol=3,
         title="SigmaR")
```

Figure 4. Temporal trend of mean (SSB/SSB_0) over `r om_sim_num` iteration runs under various combinations of steepness h and standard deviation of log recruitment sigmaR. 

## 3. Simulated population with Ricker model

### 3.1 OM_Mean with mean-unbiased stock-recruit parameters

```{r, echo=FALSE}
meanh_vec <- h_vec
logR_sd_vec <- logR_sd_vec
forloop_id <- expand.grid(meanh_vec = meanh_vec, logR_sd_vec = logR_sd_vec)

depletion_list <- list()

for(i in 1:nrow(forloop_id)){
  updated_input <- save_initial_input(base_case=FALSE,
                                      input_list=mean_base_case,
                                      case_name="mean_case",
                                      mean_R0=1000000,
                                      mean_h=forloop_id$meanh_vec[i],
                                      logR_sd=forloop_id$logR_sd_vec[i],
                                      om_bias_cor=TRUE,
                                      bias_cor_method="mean_unbiased", 
                                      SRmodel=2)
  run_om(input_list=updated_input , show_iter_num=F)
  depletion <- matrix(NA, nrow=updated_input$om_sim_num, ncol=length(updated_input$year))
  for(j in 1:updated_input$om_sim_num){
    load(file.path(updated_input$maindir, updated_input$case_name, paste("output/OM/OM", j, ".RData", sep="")))
    depletion[j,] <- om_output$SSB/(om_input$mean_R0*om_input$Phi.0)
  }
  depletion_list[[i]] <- depletion
}

save(depletion_list, file=file.path(maindir, "mean_depletion_list.RData"))
```

* Known mean $R_0$ and $h$ -> OM_Mean -> $SSB$/$S0_{mean}$
* Mean steepness $h$ tested: `r meanh_vec`
* Standard deviation of log recruitment $\sigma_R$: `r logR_sd_vec`

```{r, echo=FALSE}
load(file.path(maindir, "mean_depletion_list.RData"))
par(mfrow=c(3, 2), mar=c(4,4,1,1))
color <- rainbow(length(logR_sd_vec))
for(i in 1:length(meanh_vec)){
  plot(apply(depletion_list[[which(forloop_id$meanh_vec==meanh_vec[i])[1]]], 2, mean), ylim=c(0,2), xlab="Year", ylab="Mean SSB/SSB0", type="l", col=color[1])
  for(j in 1:length(logR_sd_vec)){
    lines(apply(depletion_list[[which(forloop_id$meanh_vec==meanh_vec[i])[j]]], 2, mean), col=color[j])
  }
  abline(h=1, col="gray", lty=2)
  legend("topleft", paste("Mean h =", meanh_vec[i]), bty="n")
}
plot.new()
legend("top", 
         legend=logR_sd_vec,
         col=color,
         lty=rep(1, length(logR_sd_vec)),
         bty="n", 
         cex=0.8,
         ncol=3,
         title="SigmaR")
```

Figure 5. Temporal trend of mean (SSB/SSB_0) over `r om_sim_num` iteration runs under various combinations of steepness h and standard deviation of log recruitment sigmaR. 

### 3.2 OM_Median with median-unbiased stock-recruit parameters

```{r, echo=FALSE}
medianh_vec <- h_vec
logR_sd_vec <- logR_sd_vec
forloop_id <- expand.grid(medianh_vec = medianh_vec, logR_sd_vec = logR_sd_vec)

depletion_list <- list()

for(i in 1:nrow(forloop_id)){
  updated_input <- save_initial_input(base_case=FALSE,
                                      input_list=mean_base_case,
                                      case_name="median_case",
                                      median_R0=1000000,
                                      median_h=forloop_id$medianh_vec[i],
                                      mean_R0=NULL,
                                      mean_h=NULL,
                                      logR_sd=forloop_id$logR_sd_vec[i],
                                      om_bias_cor=TRUE,
                                      bias_cor_method="median_unbiased", 
                                      SRmodel=2)
  run_om(input_list=updated_input , show_iter_num=F)
  depletion <- matrix(NA, nrow=updated_input$om_sim_num, ncol=length(updated_input$year))
  for(j in 1:updated_input$om_sim_num){
    load(file.path(updated_input$maindir, updated_input$case_name, paste("output/OM/OM", j, ".RData", sep="")))
    depletion[j,] <- om_output$SSB/(om_input$mean_R0*om_input$Phi.0)
  }
  depletion_list[[i]] <- depletion
}

save(depletion_list, file=file.path(maindir, "median_depletion_list.RData"))
```

* Known median $R_0$ and $h$ -> OM_Median -> $SSB$/$S0_{mean}$
* Median steepness $h$ tested: `r medianh_vec`
* Standard deviation of log recruitment $\sigma_R$: `r logR_sd_vec`

```{r, echo=FALSE}
load(file.path(maindir, "median_depletion_list.RData"))
par(mfrow=c(3, 2), mar=c(4,4,1,1))
color <- rainbow(length(logR_sd_vec))
for(i in 1:length(medianh_vec)){
  plot(apply(depletion_list[[which(forloop_id$medianh_vec==medianh_vec[i])[1]]], 2, mean), ylim=c(0,2), xlab="Year", ylab="Mean SSB/SSB0", type="l", col=color[1])
  for(j in 1:length(logR_sd_vec)){
    lines(apply(depletion_list[[which(forloop_id$medianh_vec==medianh_vec[i])[j]]], 2, mean), col=color[j])
  }
  abline(h=1, col="gray", lty=2)
  legend("topleft", paste("Median h =", medianh_vec[i]), bty="n")
}
plot.new()
legend("top", 
         legend=logR_sd_vec,
         col=color,
         lty=rep(1, length(logR_sd_vec)),
         bty="n", 
         cex=0.8,
         ncol=3,
         title="SigmaR")
```

Figure 6. Temporal trend of mean (SSB/SSB_0) over `r om_sim_num` iteration runs under various combinations of steepness h and standard deviation of log recruitment sigmaR. 

### 3.3 OM_Median with converted median-unbiased stock-recruit parameters from means

* Known mean $R_0$ and $h$ -> Convert to median $R_0$ and $h$ -> OM_Median -> $SSB$/$S0_{mean}$

```{r, echo=FALSE}
meanh_vec <- h_vec
logR_sd_vec <- logR_sd_vec
forloop_id <- expand.grid(meanh_vec = meanh_vec, logR_sd_vec = logR_sd_vec)

depletion_list <- list()
medianh_vec <- c()
medianR0_vec <- c()

for(i in 1:nrow(forloop_id)){
  updated_input <- save_initial_input(base_case=FALSE,
                                      input_list=mean_base_case,
                                      case_name="mean_case",
                                      mean_R0=1000000,
                                      mean_h=forloop_id$meanh_vec[i],
                                      logR_sd=forloop_id$logR_sd_vec[i],
                                      om_bias_cor=TRUE,
                                      bias_cor_method="median_unbiased", 
                                      SRmodel=2)
  run_om(input_list=updated_input , show_iter_num=F)
  depletion <- matrix(NA, nrow=updated_input$om_sim_num, ncol=length(updated_input$year))
  for(j in 1:updated_input$om_sim_num){
    load(file.path(updated_input$maindir, updated_input$case_name, paste("output/OM/OM", j, ".RData", sep="")))
    depletion[j,] <- om_output$SSB/(om_input$mean_R0*om_input$Phi.0)
  }
  medianh_vec[i] <- convertSRparms(R0=om_input$mean_R0, 
                              h=om_input$mean_h, 
                              phi=om_input$Phi.0, 
                              sigmaR=om_input$logR_sd, 
                              mean2med=TRUE, 
                              model=om_input$SRmodel)$hBC
  medianR0_vec[i] <- convertSRparms(R0=om_input$mean_R0, 
                              h=om_input$mean_h, 
                              phi=om_input$Phi.0, 
                              sigmaR=om_input$logR_sd, 
                              mean2med=TRUE, 
                              model=om_input$SRmodel)$R0BC
  depletion_list[[i]] <- depletion
}

forloop_id$meanR0_vec <- rep(om_input$mean_R0, nrow(forloop_id))
forloop_id$converted_medianR0 <- medianR0_vec
forloop_id$converted_medianh  <- medianh_vec
forloop_id

save(depletion_list, file=file.path(maindir, "meanmedian_depletion_list.RData"))
```

```{r, echo=FALSE}
load(file.path(maindir, "meanmedian_depletion_list.RData"))
par(mfrow=c(3, 2), mar=c(4,4,1,1))
color <- rainbow(length(logR_sd_vec))
for(i in 1:length(meanh_vec)){
  plot(apply(depletion_list[[which(forloop_id$meanh_vec==meanh_vec[i])[1]]], 2, mean), ylim=c(0,2), xlab="Year", ylab="Mean SSB/SSB0", type="l", col=color[1])
  for(j in 1:length(logR_sd_vec)){
    lines(apply(depletion_list[[which(forloop_id$meanh_vec==meanh_vec[i])[j]]], 2, mean), col=color[j])
  }
  abline(h=1, col="gray", lty=2)
  legend("topleft", paste("Mean h =", meanh_vec[i]), bty="n")
}
plot.new()
legend("top", 
         legend=logR_sd_vec,
         col=color,
         lty=rep(1, length(logR_sd_vec)),
         bty="n", 
         cex=0.8,
         ncol=3,
         title="SigmaR")
```

Figure 7. Temporal trend of mean (SSB/SSB_0) over `r om_sim_num` iteration runs under various combinations of steepness h and standard deviation of log recruitment sigmaR. 

### 3.4 OM_Mean with converted mean-unbiased stock-recruit parameters from medians

* Known median $R_0$ and $h$ -> Convert to mean $R_0$ and $h$ -> OM_Mean -> $SSB$/$S0_{mean}$

```{r, echo=FALSE}
medianh_vec <- h_vec
logR_sd_vec <- logR_sd_vec
forloop_id <- expand.grid(medianh_vec = medianh_vec, logR_sd_vec = logR_sd_vec)

depletion_list <- list()
meanh_vec <- c()
meanR0_vec <- c()

for(i in 1:nrow(forloop_id)){
  updated_input <- save_initial_input(base_case=FALSE,
                                      input_list=mean_base_case,
                                      case_name="median_case",
                                      median_R0=1000000,
                                      median_h=forloop_id$medianh_vec[i],
                                      mean_R0=NULL,
                                      mean_h=NULL,
                                      logR_sd=forloop_id$logR_sd_vec[i],
                                      om_bias_cor=TRUE,
                                      bias_cor_method="mean_unbiased", 
                                      SRmodel=2)
  run_om(input_list=updated_input , show_iter_num=F)
  depletion <- matrix(NA, nrow=updated_input$om_sim_num, ncol=length(updated_input$year))
  for(j in 1:updated_input$om_sim_num){
    load(file.path(updated_input$maindir, updated_input$case_name, paste("output/OM/OM", j, ".RData", sep="")))
    depletion[j,] <- om_output$SSB/(om_input$mean_R0*om_input$Phi.0)
  }
  depletion_list[[i]] <- depletion
  meanh_vec[i] <- convertSRparms(R0=om_input$median_R0, 
                              h=om_input$median_h, 
                              phi=om_input$Phi.0, 
                              sigmaR=om_input$logR_sd, 
                              mean2med=FALSE, 
                              model=om_input$SRmodel)$hBC
  meanR0_vec[i] <- convertSRparms(R0=om_input$median_R0, 
                              h=om_input$median_h, 
                              phi=om_input$Phi.0, 
                              sigmaR=om_input$logR_sd, 
                              mean2med=FALSE, 
                              model=om_input$SRmodel)$R0BC
}

save(depletion_list, file=file.path(maindir, "medianmean_depletion_list.RData"))

forloop_id$medianR0_vec <- rep(om_input$median_R0, nrow(forloop_id))
forloop_id$converted_meanR0 <- meanR0_vec
forloop_id$converted_meanh  <- meanh_vec
forloop_id
```

```{r, echo=FALSE}
load(file.path(maindir, "medianmean_depletion_list.RData"))
par(mfrow=c(3, 2), mar=c(4,4,1,1))
color <- rainbow(length(logR_sd_vec))
for(i in 1:length(medianh_vec)){
  plot(apply(depletion_list[[which(forloop_id$medianh_vec==medianh_vec[i])[1]]], 2, mean), ylim=c(0,2), xlab="Year", ylab="Mean SSB/SSB0", type="l", col=color[1])
  for(j in 1:length(logR_sd_vec)){
    lines(apply(depletion_list[[which(forloop_id$medianh_vec==medianh_vec[i])[j]]], 2, mean), col=color[j])
  }
  abline(h=1, col="gray", lty=2)
  legend("topleft", paste("Median h =", medianh_vec[i]), bty="n")
}
plot.new()
legend("top", 
         legend=logR_sd_vec,
         col=color,
         lty=rep(1, length(logR_sd_vec)),
         bty="n", 
         cex=0.8,
         ncol=3,
         title="SigmaR")
```

Figure 8. Temporal trend of mean (SSB/SSB_0) over `r om_sim_num` iteration runs under various combinations of steepness h and standard deviation of log recruitment sigmaR. 